Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-09 eswc-2012/phdsymp.tex
bullet list of contributions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@160 43ef1190-90fd-4dd7-a769-d0121f02b80e
Cleanup to shorten references
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@168 43ef1190-90fd-4dd7-a769-d0121f02b80e
bullett point
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@169 43ef1190-90fd-4dd7-a769-d0121f02b80e

I have not yet started to explore the scientific literature around
SPARQL Federation in any depth as I am still in an early phase of my
work. I am currently focusing my efforts on benchmarking. The
long-term goal of my work is SPARQL Federation, but that is a minor
concern in this paper.

@@

\bibliographystyle{plain-csmin}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}

>>>>

I have not yet started to explore the scientific literature around
SPARQL Federation in any depth as I am still in an early phase of my
work. I am currently focusing my efforts on benchmarking. The
long-term goal of my work is SPARQL Federation, but that is a minor
concern in this paper. Overall, the expected contributions are:

\begin{itemize}
\item Benchmarks that are able to cover all realistic
  performance-influencing parameters for SPARQL engines and make it
  possible to weigh different parameters, as well as quantify
  unexplained differences.

\item To assist optimization, enable endpoint service descriptions to
  expose:
\begin{itemize}
\item performance characteristics,
\item statistical digests of data that are optimized with respect to
  size and query performance.
\end{itemize}
\end{itemize}

@@

\bibliographystyle{plain-csmin}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{selectivity,federation,benchmarks,optimization}
